My JuliaCon proceeding

### 2023-05-25 paper.tex
Throw some pictures in

@@

@@

@@

% This is the story that I think we want to tell: you're going to run into NaNs,
% so instead of dialing the the value down, we should look for where NaNs first
% start to appear and fix those places.

@@

For our first case study, we looked at the \texttt{ShallowWaters} library,\cite{klowerNumberFormatsError2020,klowerPositsAlternativeFloats2019,klowerLowprecisionClimateComputing2021} which runs a simulates the flow of water over a seabed.
This is not a general shallow waters simulation library---it is designed primarily to showcase numerical methods involving 16-bit floats.
That said, it works for our purposes as a proving ground for FloatTracker.
We dialed the CFL parameter up to high values (as high as 10) and we started seeing NaNs in the result.

\textbf{FIXME: add pictures here}

The holes in the plots are regions where NaNs crept into the computation and destroyed the results.
In one regard, this is not as bad as a NaN kill---knowing that there are NaNs in the computation means that we have a chance to fix it.
NaN kills might silently give us the wrong answer, but we know that there were no NaN kills because our kill logs are empty.
That said, finding the source of these NaNs can be difficult.

>>>>

% If using Emacs, put cursor on last closing paren and call "eval-last-sexp" (usually `C-x C-e') to regenerate
\iffalse
(save-excursion
  (let* ((toc (funcall imenu-create-index-function))
         (headers (mapcar (pcase-lambda (`(,str . ,loc)) str)
                          toc)))
    (beginning-of-buffer)
    (search-forward (concat "%% " "--- autogenerated TOC ---"))
    (next-line)
    (beginning-of-line)
    (let ((start (point)))
      (search-forward (concat "%% " "--- end autogenerated TOC ---"))
      (beginning-of-line)
      (delete-region start (point))
      (goto-char start))
    (cl-loop for header in headers
             do (insert (format "%% %s\n" header)))
    (next-line)))
\fi

%% --- autogenerated TOC ---
% juliacon
% document
%   Introduction
%   To Kill a Floating Point
%     Where do NaNs come from?
%     NaN kills
%   FloatTracker Internals
%     Catching NaN kills
%     NaN propagation monitoring
%     NaN injection
%   Case Studies
%     Surprise NaNs: ShallowWaters
%     NaN fuzzing to find a kill: OrdinaryDiffEq
%     NaN Kills: Finch
%   Evaluation
%   Discussion
%   Related Work
%   Acknowledgments
% document
%% --- end autogenerated TOC ---

@@

% TODO?

@@

% TODO

@@

@@

For our first case study, we looked at the \texttt{ShallowWaters} library,\cite{klowerNumberFormatsError2020,klowerPositsAlternativeFloats2019,klowerLowprecisionClimateComputing2021} which runs a simulates the flow of water over a seabed.
This is not a general shallow waters simulation library---it is designed primarily to showcase numerical methods involving 16-bit floats.
That said, it works for our purposes as a proving ground for FloatTracker.
We dialed the CFL parameter up to high values (as high as 10) and we started seeing NaNs in the result.
Note that the program did not crash: instead, it began producing bad output.

\begin{figure}
  \centering
  \includegraphics[width=3in]{./fig/shallow_waters_cfl_diff.png}
  \caption{Effect of high CFL parameters: on the left, normal output. On the right: NaNs cause white holes and gaps in the result.}
  \label{fig:sw_nans}
\end{figure}

The holes in the plots are regions where NaNs crept into the computation and destroyed the results.
In one regard, this is not as bad as a NaN kill---knowing that there are NaNs in the computation means that we have a chance to fix it, whereas a NaN kill might silently give us the wrong answer.
Incidentally, we know that there were no NaN kills in this test because our kill logs are empty.
But finding the sources of NaNs can be tricky.
We expected NaNs in this case because we set the CFL parameter up so high, but tracking down the sources of NaNs generally is a difficult and time-consuming problem.
